Optimizing the Cobb Doughlas Habitability Production function using Particle Swarm Optimization

### 2017-12-01 docs/report/draft.tex
Some changes to report draft.

\usepackage[utf8]{inputenc}
\usepackage{mathtools}

@@

@@

The CDHS is estimated by maximizing the CD-PF when the returns to scale are either decreasing or constant. This is
marked by two constraints on the elasticity coefficients,
\begin{itemize}
\setlength\itemsep{0pt}
\item When $\alpha+\beta < 1$, the CD-PF observes decreasing returns to scale.
\item When $\alpha+\beta = 1$, the CD-PF observes constant returns to scale.
\end{itemize}
Further, if $0 < \alpha, \beta < 1$, the CD-PF is concave, and therefore has a maxima. The CD-PF can be adapted as a
Habitability Production Function by setting the input parameters to the measurable parameters of an exoplanet and using
these to estimate the elasticity coefficients.

@@

% Algorithm for CDHS estimation and explanation.

>>>>

\usepackage[utf8]{inputenc}
\usepackage{mathtools}
\usepackage{algorithm}
\usepackage{algpseudocode}

@@

% For algorithms
\floatname{algorithm}{Procedure}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}

@@

The CDHS is estimated by maximizing the CD-PF when the returns to scale are either decreasing or constant. This is
marked by two constraints on the elasticity coefficients,
\begin{itemize}
\setlength\itemsep{0pt}
\item When $\alpha+\beta < 1$, the CD-PF observes decreasing returns to scale (DRS).
\item When $\alpha+\beta = 1$, the CD-PF observes constant returns to scale (CRS).
\end{itemize}
Further, if $0 < \alpha, \beta < 1$, the CD-PF is concave, and therefore has a maxima. The CD-PF can be adapted as a
Habitability Production Function by setting the input parameters to the measurable parameters of an exoplanet and using
these to estimate the elasticity coefficients.

@@

\begin{algorithm}
  \begin{algorithmic}
    \Require A dataset of exoplanets with density, radius, escape velocity and surface temperature in Earth Units.
    \Ensure The $CDHS$ value for each exoplanet in the input dataset.

    \State $CDHS \gets \{\}$
    \ForAll{exoplanets $e$}
      \State $D \gets$ $e.density$
      \State $R \gets$ $e.radius$
      \State $V_e \gets$ $e.escape\_velocity$
      \State $T_s \gets$ $e.surface\_temperature$
      \\ 
      \State $Y_1 \gets \max\ D^\alpha\cdot R^\beta,\quad \text{subject to:}\quad \alpha+\beta<1;\quad 0<\alpha,\beta<1$
      \State $Y_2 \gets \max\ {V_e}^\gamma\cdot {T_s}^\delta,\quad \text{subject to:}\quad \gamma+\delta<1;\quad
      0<\gamma,\delta<1$
      \State $Y.{DRS} \gets w'\cdot Y_1\ +\ w''\cdot Y_2$
      \\
      \State $Y_1 \gets \max\ D^\alpha\cdot R^\beta,\quad \text{subject to:}\quad \alpha+\beta=1;\quad 0<\alpha,\beta<1$
      \State $Y_2 \gets \max\ {V_e}^\gamma\cdot {T_s}^\delta,\quad \text{subject to:}\quad \gamma+\delta=1;\quad
      0<\gamma,\delta<1$
      \State $Y.{CRS} \gets w'\cdot Y_1\ +\ w''\cdot Y_2$
      \\
      \State append $Y$ to $CDHS$
    \EndFor
  \end{algorithmic}
  \caption{Estimating CDHS values.}
  \label{estCDHS}
\end{algorithm}
